\texttt{GLAD-M25} - global adjoint tomography model

### 2018-09-26 gji_extraguide.tex
add workflow diagram

All the factors mentioned above will lead to a uneven distribution of
ray paths and thus uneven sampling of the earth structure. Our weighting strategy
is developed to compensate such effects. There are two terms in the misfit function
receiver weightings, $\omega_{scr}$, and source weightings $\omega_{s}$.
The calculation of both terms can be abstracted as: given the distribution of
points determine the weighting associated with each point.
Here we introduce the exponential weightings to describe the density of points and
determine the point weightings.

For more details for the weightings, please refer to the Appendix.

\subsection{Model parametrization}

Transversely isotropy model parametrization is used in our model, which is the same as GLAD-M15. Compared to a general anisotropic model which has 21 independent variables, our model could be described by 5 Love parameters,  A, C, L, N and F. In seismology, it is more straight forward to define the parameter with regarding to wavespeed. Instead of Love parameters, we have $\alpha_v$, $\alpha_h$, $\beta_v$, $\beta_h$ and $\eta$. The parameters can be further reduced to 4 assuming the radial anisotropy is due to shear anisotropy, we introduced the bulk sound speed, $c=\sqrt{\kappa/\rho}$. Our final parameters is:\\
\begin{align*}
c &= \sqrt{\kappa/\rho} \\
\beta_v &= \sqrt{L/\rho} \\
\beta_h &= \sqrt{N/\rho} \\
\eta & = F/(A-2L)
\end{align*}

The density is hard to contain in our study due to the period band we are working on. So it is constrained by isotropic shear wavespeed, $\beta = \sqrt{(2\beta_v^2 + \beta_h)/3}$,\\
\begin{equation*}
    \delta ln\rho = 0.33\delta ln\beta
\end{equation*}

@@

\begin{equation*}
    \delta \chi = \int_V (K_c\delta lnc + K_{\beta_v}\delta ln\beta_v + K_{\beta_h}\delta ln\beta_h + K\eta \delta ln\eta) dV
\end{equation*}

@@

>>>>

All the factors mentioned above will lead to a uneven distribution of
ray paths and thus uneven sampling of the earth structure. Our weighting strategy
is developed to compensate such effects. There are two terms in the misfit function
receiver weightings, $\omega_{scr}$, and source weightings $\omega_{s}$.
The calculation of both terms can be abstracted as: given the distribution of
points determine the weighting associated with each point.
Here we introduce the exponential weightings to describe the density of points and
determine the point weightings. Given a set of points $p_i$, the distance between
two is $r_{ij}$, the weightings associated with each point, $w_i$, could be obtained by:

\begin{equation}
w_{i} = \frac{1}{A} \left(
  \sum_{j=1}^N \exp \left[ \mbox{} - \left( \frac{r_{ij}} {r_{0}} \right)^2 \right] \right) ^{-1}
\label{eq:spatial_weights}
\end{equation}
where $r_{0}$ is the sensitivity distance and $A$ is the normalization term.
The reference distance will control ratios of weightings between dense and
sparse regions. For more details for the weightings, please refer to the Appendix XXX.

\subsection{Model Parametrization}
Transversely isotropy model parametrization is used in our model, same as S362ANI(GLAD-M00)
and GLAD-M15. Comparing to a general anisotropic model which has 21 independent variables,
our model could be described by 5 Love parameters, A, C, L, N and F\citep{love2013treatise}.
Since it is more straight forward to use  wavespeed as model parameters in sesimology,
we choose $\alpha_v$, $\alpha_h$, $\beta_v$, $\beta_h$ and $\eta$.
Assuming the radial anisotropy is due to shear anisotropy, these 5 parameters
can be further reduced to 4, we introduced the bulk sound speed,
$c=\sqrt{\kappa/\rho}$. Our final parameters are:\\
\begin{align*}
      c &= \sqrt{\kappa/\rho} \\
\beta_v &= \sqrt{L/\rho} \\
\beta_h &= \sqrt{N/\rho} \\
\eta & = F/(A-2L)
\end{align*}

Since density is hard to constrain due to the period band we are working on, the $\rho$ kernel is obtained by scaling the isotropic shear wavespeed kernel\citep{montagner1989petrological},\\
\begin{equation*}
    \delta ln\rho = 0.33\delta ln\beta
\end{equation*}

where $\beta$ is defined as the Voigt average of the raidally anisotropic shear wave speeds\citep{babuska1991seismic}
$$\beta = \sqrt{(2\beta_v^2 + \beta_h)/3}$$

@@

\begin{equation*}
    \delta \chi = \int_V
      (K_c\delta lnc + K_{\beta_v}\delta ln\beta_v + K_{\beta_h}\delta ln\beta_h +
      K_\eta \delta ln\eta) dV
\end{equation*}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/adjoint_workflow.pdf}
  \caption{Adjoint Tomography Workflow.}
  \label{fig:phase_hist}
\end{figure}
